### 2017-11-15 Draft2/Indexing.Growth.tex
Finish indexing

To see this, first note that $\VarIndexBuffer$ becomes $\max(\left\lceil \log_2 (i + 1) \right\rceil - \VarLogInitCapacity, 0)$. There is a constant time algorithm to compute $\left\lceil \log_2 k \right\rceil$ without using floating-point for any $k \in \mathbb{N}$, which I will not discuss because it involves concepts outside the scope of this paper. (An implementation of the algorithm, however, may be found in the links at Section \ref{sec:Implementations}.) Equipped with such an algorithm, it is easy to see that the whole expression can be computed without use of floating-point.

>>>>

% Todo: cite.
To see this, first note that $\VarIndexBuffer$ becomes $\max(\left\lceil \log_2 (i + 1) \right\rceil - \VarLogInitCapacity, 0)$. There is a constant time algorithm to compute $\left\lceil \log_2 k \right\rceil$ without using floating-point for any $k \in \mathbb{N}$, which I will not discuss because it involves concepts outside the scope of this paper. Equipped with such an algorithm, it is easy to see that the whole expression can be computed without use of floating-point.
